Supplementary material

### 2018-01-04 Manuscript/ms.tex
Cleaning up system and data

Vitoria is a coastal city and the capital of the state of Espirito Santo, Brazil, with a population of 327,801 \cite{vitpop}.
Since 2008, the company Ecovec has monitored mosquito abundance for the city using approximately 1327 sticky traps (MosquiTRAP, \cite{Eiras2009}) arranged in a grid across the city.
Each trap is checked weekly and the mosquitoes inside counted and identified, providing us with 243 weeks (2008 through week 34 of 2012) of counts of gravid female \emph{Aedes aegypti}.
Dengue is a mandatory notifiable disease, and thus the city's Ministry of Health Secretary maintains a database of weekly notified probable dengue cases (i.e., medical care sought for dengue-like symptoms) for this same time period.

To try to prevent these regular outbreaks, Vitoria and many similar cities routinely conduct mosquito control activities, often guided by mosquito surveillance data.
One source for such surveillance data is the MI-Dengue system, implemented by the company Ecovec.
This system deploys a city-wide grid of mosquito sticky traps (MosquiTRAPs) that can be used to target control in highly infested areas \cite{Eiras2009}.
This system has been shown to be effective, preventing an estimated 27,191 cases of dengue fever from 2007 - 2011 across the cities in which it was deployed \cite{Pepin2013}.
Despite this, the mosquito indices and thresholds used to prioritize control efforts remain somewhat \emph{ad-hoc}.

>>>>

Vitoria is a coastal city and the capital of the state of Espirito Santo, Brazil, with a population of 327,801 \cite{vitpop}.
Since 2008, the company Ecovec has monitored mosquito abundance for the city using approximately 1327 sticky traps (MosquiTRAP, \cite{Eiras2009}) arranged in a grid across the city.
Each trap is checked weekly and the mosquitoes inside counted and identified, with the results sent to a central database that city managers then use to map mosquito infestations and target control.
These data provide us with 243 weeks (2008 through week 34 of 2012) of total city-wide counts of trapped gravid female \emph{Aedes aegypti}.
It is important to note that this time series reflects both natural fluctuations in mosquito density and fluctuations driven by the city's existing mosquito control program.
In addition, dengue fever is a mandatory notifiable disease, and thus the city's Ministry of Health Secretary maintains a database of weekly notified probable dengue cases (i.e., medical care sought for dengue-like symptoms) for this same time period.
